Bandit Multiclass Linear Classification: \\ Efficient Algorithms for the Separable Case

### 2019-01-23 ICML-submission/algorithm-for-strongly-linearly-separable-data.tex
Fixes
Beautify section 4
Spell check

The idea behind
Algorithm~\ref{algorithm:algorithm-for-strongly-linearly-separable-examples} is
to use $K$ copies of the \textsc{Binary Perceptron} algorithm; see e.g.
\citet[Section 3.3.1]{Shalev-Shwartz-2012}. Each copy corresponds to one of the
classes. At each timestep $t$, upon seeing example $x_t$, copy $i$ makes a
binary prediction on whether $x_t$ belongs to class $i$ or not. If at least one
copy makes a positive prediction, the algorithm chooses its prediction as one of
the classes corresponding to a positive prediction. If all copies make negative
predictions, the algorithm makes a prediction uniformly at random from
$\cbr{1,\ldots,K}$.

@@

\begin{algorithm}[h]
\SetAlgoLined
\LinesNumbered
\caption{\textsc{Bandit Algorithm for Strongly Linearly Separable Examples}
\label{algorithm:algorithm-for-strongly-linearly-separable-examples}}
\textbf{Require:} Number of classes $K$, number of rounds $T$. \\
\textbf{Require:} Inner product space $(V,\ip{\cdot}{\cdot})$.  \\
\nl Initialize $w_1^{(1)} = w_2^{(1)} = \dots = w_K^{(1)} = 0$\\
\nl \For{$t=1,2,\dots,T$}{
\nl    Observe feature vector $x_t \in V$ \\
\nl    Compute $S_t = \left\{ i ~:~ 1 \le i \le K, \ \ip{w_i^{(t)}}{x_t} \ge 0 \right\}$\\
\nl    \If{$S_t = \emptyset$}{
\nl         Predict $\widehat y_t \sim \text{Uniform}(\{1,2,\dots,K\})$ \\
\nl         Observe feedback $z_t = \indicator{\widehat y_t \neq y_t}$\\
\nl          \If{$z_t = 1$}{
\nl               Set $w_i^{(t+1)} = w_i^{(t)}$, $\forall i \in \{1,2,\dots,K\}$
              }
\nl          \Else{
\nl               Set $w_i^{(t+1)} = w_i^{(t)}$, $\forall i \in \{1,2,\dots,K\} \setminus \{\widehat y_t\}$ \\
\nl Update $w_{\widehat y_t}^{(t+1)} = w_{\widehat y_t}^{(t)} + x_t$  \label{line:pos-update}
              }
        }
\nl     \Else{
\nl           Predict $\widehat y_t \in S_t$ chosen arbitrarily \\
\nl           Observe feedback $z_t  = \indicator{\widehat y_t \neq y_t}$ \\
\nl            \If{$z_t = 1$}{
\nl                Set $w_i^{(t+1)} = w_i^{(t)}$, $\forall i \in \{1,2,\dots,K\} \setminus \{\widehat y_t\}$ \\
\nl  Update $w_{\widehat y_t}^{(t+1)} = w_{\widehat y_t}^{(t)} - x_t$   \label{line:neg-update}
               }
\nl           \Else{
\nl                 Set $w_i^{(t+1)} = w_i^{(t)}$, $\forall i \in \{1,2,\dots,K\}$
           }
      }
}

@@

\begin{theorem}[Mistake lower bound]
\label{theorem:strongly-separable-examples-mistake-lower-bound}
Let $\gamma$ be a positive real number, $R$ be a non-negative real number and
let $K \le (R/\gamma)^2$ be a positive integer. Any (possibly randomized)
algorithm makes at least $((K-1)/2)\left\lfloor (R/\gamma)^2/4 \right\rfloor$
mistakes in expectation on some \textsc{Online Multiclass Classification with
Bandit Feedback} problem with $K$ classes and labeled examples $(x_1, y_1),
(x_2, y_2), \dots, (x_T, y_T) \in V \times \{1,2,\dots,K\}$ for some inner
product space $(V, \ip{\cdot}{\cdot})$ that are strongly linearly separable with
margin $\gamma$ and satisfy $\norm{x_1}, \norm{x_2}, \dots, \norm{x_T} \le R$.
\end{theorem}

@@

Algorithm~\ref{algorithm:algorithm-for-strongly-linearly-separable-examples} can
be extended to nonlinear classification using \emph{positive definite kernels}
(or \emph{kernels}, for short), which are functions of the form $k: X \times X
\to V$ for some set $X$ and inner product space $(V, \ip{\cdot}{\cdot})$ such
that the matrix $\left(k(x_i,x_j)\right)_{i,j=1}^m$ is a symmetric positive
semidefinite for any positive integer $m$ and $x_1, x_2, \dots, x_m \in X$
\citep[Definition 2.5]{Scholkopf-Smola-2002}. As opposed to explicitly
maintaining the weight vector for each class, the algorithm maintains the set of
example-scalar pairs corresponding to the updates of the non-kernelized
algorithm. As a direct consequence of
Theorem~\ref{theorem:strongly-separable-examples-mistake-upper-bound} we get a
mistake bound for the kernelized algorithm.

\begin{theorem}[Mistake upper bound for kernelized algorithm]
\label{theorem:kernelized-upper-bound}
Let $X$ be a non-empty set, let $(V, \ip{\cdot}{\cdot})$ be an inner product
space. Let $\phi:X \to V$ be a feature map and let $k:X \times X \to \R$,
$k(x,x') = \ip{\phi(x)}{\phi(x')}$ be the associated positive definite
kernel. Let $K$ be a positive integer, $\gamma$ be a positive real number, $R$
be a non-negative real number. If $(x_1, y_1), (x_2, y_2), \dots, (x_T, y_T) \in
X \times \{1,2,\dots,K\}$ are labeled examples such that:
\begin{enumerate}
\item the mapped examples $(\phi(x_1), y_1)$, $\dots$, $(\phi(x_T), y_T)$
are strongly linearly separable with margin $\gamma$,
\item for all $t$ in $\cbr{1,\ldots,T}$, $k(x_t,x_t) \le R^2$,
\end{enumerate}
then the expected number of mistakes Algorithm~\ref{algorithm:kernelized} makes
is at most $(K-1) \lfloor 4(R/\gamma)^2 \rfloor$.
\end{theorem}

>>>>

The idea behind
Algorithm~\ref{algorithm:algorithm-for-strongly-linearly-separable-examples} is
to use $K$ copies of the \textsc{Binary Perceptron} algorithm; see e.g.
\citet[Section 3.3.1]{Shalev-Shwartz-2012}. Each copy corresponds to one of the
classes. At each time step $t$, upon seeing example $x_t$, copy $i$ makes a
binary prediction on whether $x_t$ belongs to class $i$ or not. If at least one
copy makes a positive prediction, the algorithm chooses its prediction as one of
the classes corresponding to a positive prediction. If all copies make negative
predictions, the algorithm makes a prediction uniformly at random from
$\cbr{1,\ldots,K}$.

@@

\begin{algorithm}[h]
\SetAlgoLined
\LinesNumbered
\caption{\textsc{Bandit Algorithm for Strongly Linearly Separable Examples}
\label{algorithm:algorithm-for-strongly-linearly-separable-examples}}
\textbf{Require:} Number of classes $K$, number of rounds $T$. \\
\textbf{Require:} Inner product space $(V,\ip{\cdot}{\cdot})$.  \\
\nl Initialize $w_1^{(1)} = w_2^{(1)} = \dots = w_K^{(1)} = 0$\\
\nl \For{$t=1,2,\dots,T$}{
\nl    Observe feature vector $x_t \in V$ \\
\nl    Compute $S_t = \left\{ i ~:~ 1 \le i \le K, \ \ip{w_i^{(t)}}{x_t} \ge 0 \right\}$\\
\nl    \If{$S_t = \emptyset$}{
\nl         Predict $\widehat y_t \sim \text{Uniform}(\{1,2,\dots,K\})$ \\
\nl         Observe feedback $z_t = \indicator{\widehat y_t \neq y_t}$\\
\nl          \If{$z_t = 1$}{
\nl               Set $w_i^{(t+1)} = w_i^{(t)}$, $\forall i \in \{1,2,\dots,K\}$
              }
\nl          \Else{
\nl               Set $w_i^{(t+1)} = w_i^{(t)}$, $\forall i \in \{1,2,\dots,K\} \setminus \{\widehat y_t\}$ \\
\nl Update $w_{\widehat y_t}^{(t+1)} = w_{\widehat y_t}^{(t)} + x_t$  \label{line:pos-update}
              }
        }
\nl     \Else{
\nl           Predict $\widehat y_t \in S_t$ chosen arbitrarily \\
\nl           Observe feedback $z_t  = \indicator{\widehat y_t \neq y_t}$ \\
\nl            \If{$z_t = 1$}{
\nl                Set $w_i^{(t+1)} = w_i^{(t)}$, $\forall i \in \{1,2,\dots,K\} \setminus \{\widehat y_t\}$ \\
\nl  Update $w_{\widehat y_t}^{(t+1)} = w_{\widehat y_t}^{(t)} - x_t$   \label{line:neg-update}
               }
\nl           \Else{
\nl                 Set $w_i^{(t+1)} = w_i^{(t)}$, $\forall i \in \{1,2,\dots,K\}$
           }
      }
}
\end{algorithm}

@@

\begin{theorem}[Mistake lower bound]
\label{theorem:strongly-separable-examples-mistake-lower-bound}
Let $\gamma$ be a positive real number, $R$ be a non-negative real number and
let $K \le (R/\gamma)^2$ be a positive integer. Any (possibly randomized)
algorithm makes at least $((K-1)/2)\left\lfloor (R/\gamma)^2/4 \right\rfloor$
mistakes in expectation on some sequence of labeled examples $(x_1, y_1),
(x_2, y_2), \dots, (x_T, y_T) \in V \times \{1,2,\dots,K\}$ for some inner
product space $(V, \ip{\cdot}{\cdot})$ such that the examples are strongly
linearly separable with margin $\gamma$ and satisfy $\norm{x_1}, \norm{x_2},
\dots, \norm{x_T} \le R$.
\end{theorem}

@@

Algorithm~\ref{algorithm:algorithm-for-strongly-linearly-separable-examples} can
be extended to nonlinear classification using \emph{positive definite kernels}
(or \emph{kernels}, for short), which are functions of the form $k: X \times X
\to \R$ for some set $X$ such that the matrix
$\left(k(x_i,x_j)\right)_{i,j=1}^m$ is a symmetric positive semidefinite for any
positive integer $m$ and $x_1, x_2, \dots, x_m \in X$ \citep[Definition
2.5]{Scholkopf-Smola-2002}.\footnote{Every kernel has an associated feature map
$\phi:X \to V$ for some inner product space $(V,\ip{\cdot}{\cdot})$ such that
$k(x,x') = \ip{\phi(x)}{\phi(x')}$.} As opposed to explicitly maintaining the
weight vector for each class, the algorithm maintains the set of example-scalar
pairs corresponding to the updates of the non-kernelized algorithm. As a direct
consequence of
Theorem~\ref{theorem:strongly-separable-examples-mistake-upper-bound} we get a
mistake bound for the kernelized algorithm.

\begin{theorem}[Mistake upper bound for kernelized algorithm]
\label{theorem:kernelized-upper-bound}
Let $X$ be a non-empty set, let $(V, \ip{\cdot}{\cdot})$ be an inner product
space. Let $\phi:X \to V$ be a feature map and let $k:X \times X \to \R$,
$k(x,x') = \ip{\phi(x)}{\phi(x')}$ be the associated positive definite
kernel. Let $K$ be a positive integer, $\gamma$ be a positive real number, $R$
be a non-negative real number. If $(x_1, y_1), (x_2, y_2), \dots, (x_T, y_T) \in
X \times \{1,2,\dots,K\}$ are labeled examples such that:
\begin{enumerate}
\item the mapped examples $(\phi(x_1), y_1)$, $\dots$, $(\phi(x_T), y_T)$
are strongly linearly separable with margin $\gamma$,
\item $k(x_1, x_1), k(x_2, x_2), \dots, k(x_T,x_T) \le R^2$,
\end{enumerate}
then the expected number of mistakes Algorithm~\ref{algorithm:kernelized} makes
is at most $(K-1) \lfloor 4(R/\gamma)^2 \rfloor$.
\end{theorem}

### 2019-01-23 ICML-submission/introduction.tex
removed chicheng's comment
Fixes

We study the problem of \textsc{Online Multiclass Linear Classification with
Bandit Feedback}~\citep{Kakade-Shalev-Shwartz-Tewari-2008}. The problem can be
viewed as a repeated game between a learner and an adversary. At each time step
$t$, the adversary chooses a labeled example $(x_t, y_t)$ and reveals $x_t\in
\R^d$ to the learner. Upon receiving $x_t$, the learner makes a prediction
$\widehat{y}_t$ and receives feedback. In contrast with the standard
full-information setting, where the feedback given is the correct label $y_t$,
here the feedback is only a binary indicator of whether the prediction was
correct or not. The protocol of the problem is formally stated below.

@@

In Appendix~\ref{section:nearest-neighbor-algorithm}, we propose and analyze a
very different algorithm for weakly separable data. The algorithm is based on
the obvious idea that two points that are close enough must have the same label.
\chicheng{I wonder if the mistake bound of this algorithm is too large to be included
as ``our contributions'' - perhaps we should only mention it as a folklore/baseline?}

Finally, we study two questions related to the computational and
information-theoretic hardness of the problem. Any algorithm for the bandit
setting collects information in the form of so called \emph{strongly labeled}
and \emph{weakly labeled} examples. Strongly labeled examples are those for
which we know the class label. Weakly labeled example is an example for which we
know that class label can be anything except for a particular one class. In
Appendix~\ref{section:np-hardness-of-weak-labeling-problem}, we show that the
offline problem of finding a multiclass linear classifier consistent with a set
of strongly and weakly labeled examples is NP-hard. In
Appendix~\ref{section:mistake-lower-bound-for-ignorant-algorithms}, we prove a
lower bound on the number of mistakes of any algorithm that uses only
strongly-labeled examples and ignores weakly labeled examples.

>>>>

We study the problem of \textsc{Online Multiclass Linear Classification with
Bandit Feedback}~\citep{Kakade-Shalev-Shwartz-Tewari-2008}. The problem can be
viewed as a repeated game between a learner and an adversary. At each time step
$t$, the adversary chooses a labeled example $(x_t, y_t)$ and reveals the
feature vector $x_t$ to the learner. Upon receiving $x_t$, the learner makes a
prediction $\widehat{y}_t$ and receives feedback. In contrast with the standard
full-information setting, where the feedback given is the correct label $y_t$,
here the feedback is only a binary indicator of whether the prediction was
correct or not. The protocol of the problem is formally stated below.

@@

In Appendix~\ref{section:nearest-neighbor-algorithm}, we propose and analyze a
very different algorithm for weakly linearly separable data. The algorithm is
based on the obvious idea that two points that are close enough must have the
same label.
%\chicheng{I wonder if the mistake bound of this algorithm is too large to be included
%as ``our contributions'' - perhaps we should only mention it as a folklore/baseline?}

Finally, we study two questions related to the computational and
information-theoretic hardness of the problem. Any algorithm for the bandit
setting collects information in the form of so called \emph{strongly labeled}
and \emph{weakly labeled} examples. Strongly labeled examples are those for
which we know the class label. Weakly labeled example is an example for which we
know that class label can be anything except for one particular class. In
Appendix~\ref{section:np-hardness-of-weak-labeling-problem}, we show that the
offline problem of finding a multiclass linear classifier consistent with a set
of strongly and weakly labeled examples is NP-hard. In
Appendix~\ref{section:mistake-lower-bound-for-ignorant-algorithms}, we prove a
lower bound on the number of mistakes of any algorithm that uses only
strongly-labeled examples and ignores weakly labeled examples.

### 2019-01-23 ICML-submission/related-work.tex
polished the experiment section
Fixes

The problem of online bandit multiclass learning was initially formulated in the
pioneering work of~\citet{Auer-Long-1999}, under the name of ``weak
reinforcement model''. They showed that if all examples agree with some
classifier from a prespecified hypothesis class $\calH$, then the optimal
mistake bound in the bandit setting can be upper bounded by the optimal mistake
bound in the full information setting, times a factor of $(2.01 + o(1))K \ln K$.
\citet{Long-2017} later improved the factor to $(1 + o(1)) K \ln K$ and showed
its near-optimality. \citet{Daniely-Helbertal-2013} extended the results to the
setting where the performance of the algorithm is measured by its regret, i.e.
the difference between the number of mistakes made by the algorithm and the
number of mistakes made by the best classifier in $\calH$ in hindsight.
We remark that
all algorithms developed in this context are computationally inefficient.

The linear classification version of this problem is initially studied
by~\citet{Kakade-Shalev-Shwartz-Tewari-2008}. They proposed two computationally
inefficient algorithms that work in the weakly linearly separable setting, one
with a mistake bound of
$O(K^2 d \ln(d/\gamma))$,
the other with a
mistake bound of $\widetilde{O}((K^2/\gamma^2) \ln T)$. The latter result
was later improved by \citet{Daniely-Helbertal-2013}, which gives a
computationally inefficient algorithm with a mistake upper bound of
$\widetilde{O}(K/\gamma^2)$.
In addition, the authors propose the
\textsc{Banditron} algorithm, a computationally efficient algorithm that has a
$O(T^{2/3})$ regret against the multiclass hinge loss in the general setting,
and has a $O(\sqrt{T})$ mistake bound in the $\gamma$-weakly linearly separable
setting.
In contrast to mild dependencies on the time horizon for mistake bounds of
computationally inefficient algorithms,
the polynomial dependence of \textsc{Banditron}'s mistake bound on the
time horizon is undesirable for problems with a long time horizon, in the
weakly linearly separable setting. One key open
question left by~\citet{Kakade-Shalev-Shwartz-Tewari-2008} is whether one can
design computationally efficient algorithms that achieve mistake bounds that
match or improve over those of inefficient algorithms. In this paper, we take a
step towards answering this question, showing that efficient algorithms with
mistake bounds quasipolynomial in $1/\gamma$ (for constant $K$)
or quasipolynomial in $K$ (for constant $\gamma$) can be obtained.

@@

%Online bandit multiclass learning is a special case of the contextual bandits
%problem~\citep{Auer-2003, Langford-Zhang-2008}, where the cost is the
%classification error. A series of works in the contextual bandits literature
%focuses on oracle-efficiency, that is, they assume access to an oracle that
%given a set of cost-sensitve learning examples, generates .

There is a large body of literature on the contextual bandits
problem~\citep{Auer-2003, Langford-Zhang-2008}. In this problem, the learner is
given a policy class $\Pi$, and at each timestep $t$, an example $x_t$ is shown,
with an associated cost vector $c_t$ hidden. The learner then takes an action
$\widehat{y}_t$, and observes the incurred cost $c_t(\widehat{y}_t)$. The goal
of the learner is to minimize its regret $\sum_{t=1}^T c_t(\widehat{y}_t) -
\min_{\pi \in \Pi} \sum_{t=1}^T c_t(\pi(x_t))$.
%%%%%
The bandit multiclass
learning problem can be seen as a special case,
% of the contextual bandits problem,
where the
cost $c_t(i)$ is the classification error $\indicator{i \neq y_t}$, and the
policy class $\Pi$ is the set of linear classifiers $\cbr{x \mapsto \argmax_y
(Wx)_y: W \in \R^{k \times d}}$. A series of works in the contextual bandits
learning literature
%focus on oracle-efficiency~\citep{Dudik-Hsu-Kale-Karampatziakis-Langford-Reyzin-Zhang-2011,
%Agarwal-Hsu-Kale-Langford-Li-Schapire-2014, Rakhlin-Sridharan-2016,
%Syrgkanis-Krishnamurthy-Schapire-2016,
%Syrgkanis-Luo-Krishnamurthy-Schapire-2016}. Specifically, they
assume access to
a policy optimization oracle that returns a policy in $\Pi$ that minimizes
its empirical cost on any set of cost-sensitive examples, and
%the
construct algorithms that call
%algorithm only calls
the oracle a polynomial number of times%
~\citep{Dudik-Hsu-Kale-Karampatziakis-Langford-Reyzin-Zhang-2011,
Agarwal-Hsu-Kale-Langford-Li-Schapire-2014, Rakhlin-Sridharan-2016,
Syrgkanis-Krishnamurthy-Schapire-2016,
Syrgkanis-Luo-Krishnamurthy-Schapire-2016}.
%%%%%
However, these algorithms are not
truly computationally efficient in our setting, as it is NP-hard in general to
find a linear classifier that minimizes the empirical cost over a set of
examples~\citep{Arora-Babai-Stern-Sweedyk-1997}.

%that receives a set of cost-sensitive learning examples and policy class $\Pi$,
%as algorithms generate cost-sensitive examples that may not be linearly
%separable Algorithms that satisfy oracle efficiency has been proposed in the
%literature, for example.

Recently, \citet{Foster-Krishnamurthy-2018} developed a rich theory of
contextual bandits with surrogate losses, focusing on regrets of the form
$\sum_{t=1}^T c_t(\widehat{y}_t) - \min_{f \in \calF} \sum_{t=1}^T \frac{1}{K}
\sum_{i=1}^K c_t(i) \phi( f_i(x_t) )$, where $\calF$ contains score functions
$f$ such that $\sum_{i=1}^K f_i(\cdot) \equiv 0$, and $\phi(s) = \max(1 - \frac
s \gamma, 0)$ or $\min(1, \max(1 - \frac s \gamma, 0))$. On one hand, it gives
information-theoretic regret upper bounds
%%%%%
%under
 for
%%%%%
various settings of $\calF$. On the other hand, it gives an efficient algorithm
%%%%%
with an
%%%%%
$O(\sqrt{T})$ regret against the benchmark of
$\calF = \cbr{x \mapsto W x: W \in \R^{k \times d}, \one^T W = 0}$. A direct
application of this result to \textsc{Online Bandit Multiclass Linear
Classification}
%%%%%
%yields
gives
%%%%%
an algorithm with $O(\sqrt{T})$ mistake bound in the
strongly linearly separable %%%%%
case.
%%%%%

>>>>

The problem of online bandit multiclass learning was initially formulated in the
pioneering work of~\citet{Auer-Long-1999} under the name of ``weak reinforcement
model''. They showed that if all examples agree with some classifier from a
prespecified hypothesis class $\calH$, then the optimal mistake bound in the
bandit setting can be upper bounded by the optimal mistake bound in the full
information setting, times a factor of $(2.01 + o(1))K \ln K$. \citet{Long-2017}
later improved the factor to $(1 + o(1)) K \ln K$ and showed its
near-optimality. \citet{Daniely-Helbertal-2013} extended the results to the
setting where the performance of the algorithm is measured by its regret, i.e.
the difference between the number of mistakes made by the algorithm and the
number of mistakes made by the best classifier in $\calH$ in hindsight. We
remark that all algorithms developed in this context are computationally
inefficient.

The linear classification version of this problem is initially studied
by~\citet{Kakade-Shalev-Shwartz-Tewari-2008}. They proposed two computationally
inefficient algorithms that work in the weakly linearly separable setting, one
with a mistake bound of $O(K^2 d \ln(d/\gamma))$, the other with a mistake bound
of $\widetilde{O}((K^2/\gamma^2) \ln T)$. The latter result was later improved
by \citet{Daniely-Helbertal-2013}, which gives a computationally inefficient
algorithm with a mistake upper bound of $\widetilde{O}(K/\gamma^2)$. In
addition,~\citet{Kakade-Shalev-Shwartz-Tewari-2008} propose the
\textsc{Banditron} algorithm, a computationally efficient algorithm that has a
$O(T^{2/3})$ regret against the multiclass hinge loss in the general setting,
and has a $O(\sqrt{T})$ mistake bound in the $\gamma$-weakly linearly separable
setting. In contrast to mild dependencies on the time horizon for mistake bounds
of computationally inefficient algorithms, the polynomial dependence of
\textsc{Banditron}'s mistake bound on the time horizon is undesirable for
problems with a long time horizon, in the weakly linearly separable setting. One
key open question left by~\citet{Kakade-Shalev-Shwartz-Tewari-2008} is whether
one can design computationally efficient algorithms that achieve mistake bounds
that match or improve over those of inefficient algorithms. In this paper, we
take a step towards answering this question, showing that efficient algorithms
with mistake bounds quasipolynomial in $1/\gamma$ (for constant $K$) or
quasipolynomial in $K$ (for constant $\gamma$) can be obtained.

@@

There is a large body of literature on the contextual bandits
problem~\citep{Auer-2003, Langford-Zhang-2008}. In this problem, the learner is
given a policy class $\Pi$, and at each timestep $t$, an example $x_t$ is shown,
with an associated cost vector $c_t$ hidden. The learner then takes an action
$\widehat{y}_t$, and observes the incurred cost $c_t(\widehat{y}_t)$. The goal
of the learner is to minimize its regret $\sum_{t=1}^T c_t(\widehat{y}_t) -
\min_{\pi \in \Pi} \sum_{t=1}^T c_t(\pi(x_t))$. The bandit multiclass learning
problem can be seen as a special case, where the cost $c_t(i)$ is the
classification error $\indicator{i \neq y_t}$, and the policy class $\Pi$ is the
set of linear classifiers $\cbr{x \mapsto \argmax_y (Wx)_y: W \in \R^{k \times
d}}$. A series of works in the contextual bandits learning literature assume
access to a policy optimization oracle that returns a policy in $\Pi$ that
minimizes its empirical cost on any set of cost-sensitive examples, and
construct algorithms that call the oracle a polynomial number of times%
~\citep{Dudik-Hsu-Kale-Karampatziakis-Langford-Reyzin-Zhang-2011,
Agarwal-Hsu-Kale-Langford-Li-Schapire-2014, Rakhlin-Sridharan-2016,
Syrgkanis-Krishnamurthy-Schapire-2016,
Syrgkanis-Luo-Krishnamurthy-Schapire-2016}. However, these algorithms are not
truly computationally efficient in our setting, as it is NP-hard in general to
find a linear classifier that minimizes the empirical cost over a set of
examples~\citep{Arora-Babai-Stern-Sweedyk-1997}.

Recently, \citet{Foster-Krishnamurthy-2018} developed a rich theory of
contextual bandits with surrogate losses, focusing on regrets of the form
$\sum_{t=1}^T c_t(\widehat{y}_t) - \min_{f \in \calF} \sum_{t=1}^T \frac{1}{K}
\sum_{i=1}^K c_t(i) \phi( f_i(x_t) )$, where $\calF$ contains score functions
$f$ such that $\sum_{i=1}^K f_i(\cdot) \equiv 0$, and $\phi(s) = \max(1 - \frac
s \gamma, 0)$ or $\min(1, \max(1 - \frac s \gamma, 0))$. On one hand, it gives
information-theoretic regret upper bounds for various settings of $\calF$. On
the other hand, it gives an efficient algorithm with an $O(\sqrt{T})$ regret
against the benchmark of $\calF = \cbr{x \mapsto W x: W \in \R^{k \times d},
\one^T W = 0}$. A direct application of this result to \textsc{Online Bandit
Multiclass Linear Classification} gives an algorithm with $O(\sqrt{T})$ mistake
bound in the strongly linearly separable case.
